title

### 2024-10-16 index.qmd
modified .gitignore and index.qmd

---
title: title
authors:
  - name: Norah Jones
    affiliation: The University
    roles: writing
    corresponding: true
bibliography: references.bib
---

>>>>

---
title: title
shorttitle: A Short title # aog-article-pdf
shortauthors: Isaiah      # aog-article-pdf
authors:
  - name: Isaiah Espinoza
    email: gespinoz@umd.edu
    roles: author
    corresponding: true
affiliations:
  - id: uni
    name: University of Maryland
    department: Department of Government and Politics
reference-section-title: Bibliography
date: "2024-10-16"
---
